---
title: Basics
output: 
  html_document: 
    theme: darkly

        
---
```{r eval = FALSE}
library(AER)
library(tidyverse)
```

## Section 1

Summary - Returns some basic summary statistics such as min, max, mean, median. Minimum input is an object.
Str - Returns the structure of the specified object. Minimum input is an Object.
Names - Returns the names of a vector if available and return NULL if there are no assigned names. Minimum input is an object variable.
Glimpse - Similar to str but also returns the first x amount values of the object. Minimum input is an object.
LM - Runs and return the results of a linear model regression. Minimum input is the formula and a data frame.

## Section 2

```{r}
x<- 3+8
y<- 4/5
z<- 2+x^2
variables<-c(x,y,z)
big<- variables>1
big


```

## Section 3

```{r}
a <- c(1:10)
a + 3
a ^ 3
b <- c(1:10)
a + b
a ^ b
c <- c(a,b)
```

## Section 4

```{r eval=FALSE}
x <- rnorm(100, mean = 10)
e <- rnorm(100)
y <- 3+ 2*x + e
lab_data_df <- data.frame(x,y)
lm(y~x,lab_data_df)
```
The $\beta_0$ is slighty lower than the expected  value of 3 but still within a reasonable standard deviation. The $\beta_1$ is right on the expected value of 2.
```{r eval=FALSE}
xsdbig <- rnorm(100, mean = 10, sd = 20)
esdbig <- rnorm(100, sd = 20)
ysdbig <- 3+ 2*xsdbig + esdbig
lab_data_df_sdbig <- data.frame(xsdbig,ysdbig)
lm(ysdbig ~ xsdbig,lab_data_df_sdbig)

xsdsm <- rnorm(100, mean = 10, sd = .1)
esdsm <- rnorm(100, sd = .1)
ysdsm <- 3+ 2*xsdsm + esdsm
lab_data_df_sdsm <- data.frame(xsdsm,ysdsm)
lm(ysdsm~xsdsm,lab_data_df_sdsm)
```
Changing the standard deviation affects our $\beta_0$ and our error term. This causes our predicted value to be less accurate when the standard deviation is increased and more accurate when the standard deviation is decreased.

## Section 5

```{r message = FALSE}
library(haven)
nlsy97_s20 <- read_dta("C:/Users/Corey/Documents/GitHub/data/nlsy97_s20.dta")
View(nlsy97_s20)
```

```{r message = FALSE}
library(readxl)
X2019nflsalaries <- read_excel("C:/Users/Corey/Documents/GitHub/data/2019nflsalaries.xlsx")
View(X2019nflsalaries)
```

```{r message = FALSE}
library(tidyverse)
names(nlsy97_s20)
summary(nlsy97_s20$female)
age <- 2015 - nlsy97_s20$bdate_y_1997
age2 <- age^2
ggplot(nlsy97_s20, aes(x = nlsy97_s20$income_gross_yr_1997, y = nlsy97_s20$income_2015)) + geom_point()

```

```{r }
mean(X2019nflsalaries$Salary)
summary(as.factor(X2019nflsalaries$Pos))
```
#The Wide Receiver position has the most salaried players
```{r }
Salariesinmillions<- X2019nflsalaries$Salary/1000000
ggplot(X2019nflsalaries, aes(Salariesinmillions)) + geom_density()

```
```{r}
teamsalaries <- aggregate(X2019nflsalaries$Salary ~ X2019nflsalaries$Tm, X2019nflsalaries, sum)
teamsalaries
```

